Atomify - a live LAMMPS visualizer

### 2017-06-16 ms.tex
Merge

@@

\begin{figure}
	\centering
	\includegraphics[width=0.3\textwidth]{dashboard.png}
	\caption{Dashboard}
	\label{fig:dashboard}
\end{figure}

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{figures/data-pipeline.pdf}
	\caption{Rendering in Atomify is based on modifying the data from LAMMPS
    by coloring, producing periodic images, and generating bonds between atoms.
    The data is extracted from LAMMPS using the library API and by accessing
    the core classes.}
	\label{fig:data-pipeline}
\end{figure}

The data pipeline from LAMMPS to rendering in Atomify is illustrated in figure
\ref{fig:data-pipeline}.
When rendering one often wants to modify the data from LAMMPS before it is
visualized.
Examples are periodic images of the simulation,
slicing and coloring.
We have been inspired by the pipeline used in Ovito where the data flows through
several \textit{modifiers}, each modifying the visualization data before the
data is converted to a format for the GPU.

\subsection{Rendering techniques}

@@

The simple case study showed how Atomify can be used for quick iteration in

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{final_billboard.png}
	\caption{TODO: Overview of workflow, going from script, to simulation, to analyzing data, to results}
	\label{fig:gui}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.3\textwidth]{dashboard.png}
	\caption{Dashboard}
	\label{fig:gui}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{final_billboard.png}
	\caption{TODO: How data flows from LAMMPS to Atomify, technically}
	\label{fig:gui}
\end{figure}

@@

\subsection{Live plotting}

Live plotting is implemented using Qt Charts and Qt Data Visualization,
which are part of the Qt framework.
The data is extracted using LAMMPS' C++ API and converted to Qt datatypes before
visualization.

\subsection{Data pipeline}

When rendering one often wants to modify the data
from LAMMPS before it is visualized.
Examples are periodic images of the simulation,
slicing and coloring.
We have been inspired by the pipeline used in Ovito where the data flows through
several \textit{modifiers}, each modifying the visualization data before the
data is converted to a format for the GPU.

\section{Rendering techniques}

@@
